Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Hot fix...

Now consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}. First,
the only source use the exact same definition as ours is written by
Jamison and Lodwick~\cite{JamisonLodwick2004}. They introduced a
definition of integration as follow\footnote{\yutsung{Although they said they would explore their integration
in more details, they change their definition of IVPM later. Hence,
I don't know if they have any further development of their integration.}}. If we denote the indicator function by 
\begin{equation} 
\mathbf{1}_{A}(x)=\cases{ 
1 & if $x\in A$ ;\\ 
0 & if $x\notin A$, 
}
\end{equation}
then given a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{A_{i}}$,
where $x_{i}$ are all different, the integral of $X$ is defined
by 
\begin{eqnarray*}
\int_{A}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)}\right]\textrm{ .}
\end{eqnarray*}
For example, $X_{0}=0\cdot\mathbf{1}_{\{HH\}}+1\cdot\mathbf{1}_{\{HT,TH\}}+2\cdot\mathbf{1}_{\{TT\}}$,
and $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$. Therefore, 
\begin{eqnarray*}
\int_{\Omega}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1}\right]\\
 & = & \left[\inf\set{a_{1}+2a_{2}}{a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{1}+a_{2}=1},\right.\\
 &  & \left.\sup\set{a_{1}+2a_{2}}{a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{1}+a_{2}=1}\right]\\
 & = & \left[\inf\set{a_{1}+2a_{2}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{1}+a_{2}=1},\right.\\
 &  & \left.\sup\set{a_{1}+2a_{2}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{1}+a_{2}=1}\right]\\
 & = & \left[\inf\set{a_{1}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{1}=1},\right.\\
 &  & \left.\sup\set{a_{1}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{1}=1}\right]\\
 & = & \left[1,1\right]
\end{eqnarray*}
What does this means...?

>>>>

Now consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}. First,
the only source use the exact same definition as ours is written by
Jamison and Lodwick~\cite{JamisonLodwick2004}. They introduced a
definition of integration as follow\footnote{\yutsung{Although they said they would explore their integration
in more details, they change their definition of IVPM later. Hence,
I don't know if they have any further development of their integration.}}. If we denote the indicator function by 
\begin{equation} 
\mathbf{1}_{A}(x)=\cases{ 
1 & if $x\in A$ ;\\ 
0 & if $x\notin A$, 
}
\end{equation}
then given a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{A_{i}}$,
where $x_{i}$ are all different, the integral of $X$ is defined
by 
\begin{eqnarray*}
\int_{A}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)}\right]\textrm{ .}
\end{eqnarray*}
For example, $X_{0}=0\cdot\mathbf{1}_{\{HH\}}+1\cdot\mathbf{1}_{\{HT,TH\}}+2\cdot\mathbf{1}_{\{TT\}}$,
and $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$. Therefore, 
\begin{eqnarray*}
\int_{\Omega}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1}\right]\\
 & = & \left[\inf\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
 &  & \left.\sup\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
 & = & \left[\inf\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
 &  & \left.\sup\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
 & = & \left[\inf\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1},\right.\\
 &  & \left.\sup\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1}\right]\\
 & = & \left[\frac{1}{2},1\right]
\end{eqnarray*}
What does this means...?
